Autogenerated Questions Paper Draft

### 2018-05-26 paper_draft/paper_draft.tex
Add lists to enumerated concepts

@@

TODO: do a fancy list thing here
Producing unique answers can become complicated is for two reasons: i) each category generates its own distractors using ``clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes) and ii) complex answers
(in particular, answers containing vectors as in \textbf{Arrays}) become more difficult to compare and even more difficult
to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
In the case of (i), it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of (ii), if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see \textbf{Arrays Difficulty 3} in section \ref{subsubsec-arrays}). 
It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

@@

TODO: another fancy list thing here
There are four essential components we wish to answer with each of these categories: a) what is the goal of the question; what is it asking? b) an example question
(removed from GIFT format) for easy reference, c) what parts of the question are random? which of those parts are essential to the question (i.e. what
parts affect the answer or structure of the question)? which of those parts are non-essential (i.e. what parts have no affect over the question whatsoever)?
and are there any essential parts of the question that are not randomized (i.e. are there any constant factors of the question)? and lastly d) what methods
are used to generate the distractors? It is important to ask (a) so each question can have a definitive objective, and it should be easy to note if
certain randomness adds/hinders that objective or if the randomness does not preserve a comparable difficulty for different students.
This basically tries to prevent elements making a question ``too random". It is also important to ask [TODO: should I include this part c? is it talked about enough later on?] (c) for a deep understanding of how the question
is randomized -- and how some parts are kept constant -- to produce independent yet similarly difficult questions. This part answers the main
methodology of all question generation. And as a consequence, (d) becomes relevant to ask to offer convincing distractors for a cohesive question.

@@

TODO: fancy list thing below

In this instance, the four distractor methods alter how the expression is evaluated by 1) disregarding order of operations, 2) using float values and operations, 3) evaluating the expression from
right to left, and 4) disregarding the order of operations and using the float values (a combination of 1 and 2). These methods, while not particularly novel or sophisticated, aid the main objective 
of the question in their deliberate misunderstanding of the main concepts. For example, any student that is unfamiliar with integer operations is certain to select the distractor provided by method 2. Of course, in some cases, certain methods would not provide a different answer than the correct one (as integer addition and float addition are similar, etc.), however different answers are still guaranteed by the unique answer checking (see Unique Answer Guarantee in section \ref{sec-unique_answer_guarantee}).

@@

TODO: decide about list thing

As for distractor methods, this question uses methods similar to the first difficulty (which are also similar to those in \textbf{Expressions}), but the most interesting methods here include i) evaluating the expression with all float operations (regardless of any previous type coercion), ii) evaluating the expression with all the original float values (essentially ignoring type coercion), and iii) using the floor of the correct answer (to provide an integer-like answer). Of course, as this question is furthered, these methods will have to be slightly altered to try and provide more convincing distractors in a general case (as in an arbitrary number of operands or an arbitrary return type).

@@

TODO: list thing

The next research that should take place is in regards to actual use of the system that produces quantitative results. Any statistics would not only be helpful in evaluating the system as a whole, but also useful in identifying a) the efficacy of each category, b) a statistically-based distinction between difficulties within categories, and c) efficacy of certain distractor methods for a question. With these results, this system (and other systems) would be better able to produce and classify the questions within them, as well as produce more effective distractor methods. However, there are some ethical problems that will need to be addressed in some of this work. Namely, any test for difficulty between students may cause lower test scores than usual or what is considered ``fair", which adversely and unintentionally affects students.

>>>>

\usepackage{enumitem}

@@

Producing unique answers can become complicated is for two reasons: 
\begin{enumerate}[label=\textbf{(\arabic*)}]
\item \label{enum-unique_1} Each category generates its own distractors using ``clever" methods (e.g. evaluating an expression
without order of operations, or evaluating an expression based on wrong datatypes). 
\item \label{enum-unique_2} Complex answers (in particular, answers containing vectors as in \textbf{Arrays}) become more difficult to compare and even more difficult to generate an arbitrary new distractor (for the sake of uniqueness) that is still a somewhat plausible answer.
\end{enumerate}
In the case of \ref{enum-unique_1}, it is fairly simple to compare all answers, and any distractors that are not unique are reassigned
a random value close to the answer. This is usually done with computational questions where the answer is simply a
numerical value. However, in the case of \ref{enum-unique_2}, if we were to simply alter a value in the vector, the distractor would
become completely implausible because the answer only contains values that are originally in the array (see \textbf{Arrays Difficulty 3} in section \ref{subsubsec-arrays}). 
It would make no sense at all to change a value in the array. In order to generate distractors that
are still plausible (but are guaranteed to be unique), we can simply shuffle the order of the vector. Yet, this has
another precondition that the number of permutations for the correct answer must be greater than or equal to the
number of available answers. Without this restraint, there would not be enough unique answers. If this is not met,
then it suffices to revert to the original strategy and simply assign a random value to the vector. Although it may
not be very convincing, unique distractors take precedence over plausible ones.

@@

There are four essential components we wish to answer with each of these categories: 
\begin{enumerate}[label=\textbf{(\arabic*)}]
\item \label{enum-categories_1}
What is the goal of the question; what is it asking? 
\item \label{enum-categories_2}
An example question
(in both GIFT and rendered format) for reference.
\item \label{enum-categories_3}
What parts of the question are random? Furthermore, which of those parts are essential to the question (i.e. what
parts affect the answer or structure of the question), and which of those parts are non-essential (i.e. what parts have no affect over the question whatsoever)?
Are there any essential parts of the question that are not randomized (i.e. are there any constant factors)?
\item \label{enum-categories_4}
What methods
are used to generate the distractors? 
\end{enumerate}
It is important to ask \ref{enum-categories_1} so each question can have a definitive objective, and it should be easy to note if
certain randomness adds/hinders that objective or if the randomness does not preserve a comparable difficulty for different students.
This basically tries to prevent elements making a question ``too random". It is also important to ask [TODO: should I include this part \ref{enum-categories_3}? is it talked about enough later on?] \ref{enum-categories_3} for a deep understanding of how the question
is randomized -- and how some parts are kept constant -- to produce independent yet similarly difficult questions. This part answers the main
methodology of all question generation. And as a consequence, \ref{enum-categories_4} becomes relevant to ask to offer convincing distractors for a cohesive question.

@@

In this instance, the four distractor methods alter how the expression is evaluated by:
\begin{enumerate}[label=\textbf{(\arabic*)}]
\item \label{enum-expr_1}
Disregarding order of operations 
\item \label{enum-expr_2}
Using float values and operations
\item \label{enum-expr_3}
Evaluating the expression from right to left 
\item \label{enum-expr_4}
Disregarding the order of operations and using the float values (a combination of \ref{enum-expr_1} and \ref{enum-expr_2})
\end{enumerate}
These methods, while not particularly novel or sophisticated, aid the main objective 
of the question in their deliberate misunderstanding of the main concepts. For example, any student that is unfamiliar with integer operations is certain to select the distractor provided by method \ref{enum-expr_2} . Of course, in some cases, certain methods would not provide a different answer than the correct one (as integer addition and float addition are similar, etc.), however different answers are still guaranteed by the unique answer checking (see Unique Answer Guarantee in section \ref{sec-unique_answer_guarantee}).

@@

As for distractor methods, this question uses methods similar to the first difficulty (which are also similar to those in \textbf{Expressions}), but the most interesting methods here include:
\begin{enumerate}[label=\textbf{(\arabic*)}]
\item
Evaluating the expression with all float operations (regardless of any previous type coercion) 
\item
Evaluating the expression with all the original float values (essentially ignoring type coercion)
\item
Using the floor of the correct answer (to provide an integer-like answer)
\end{enumerate}
Of course, as this question is furthered, these methods will have to be slightly altered to try and provide more convincing distractors in a general case (as in an arbitrary number of operands or an arbitrary return type).

@@

The next research that should take place is in regards to actual use of the system that produces quantitative results. Any statistics would not only be helpful in evaluating the system as a whole, but also useful in identifying: 
\begin{enumerate}[label=\textbf{(\arabic*)}]
\item
The efficacy of each category
\item
A statistically-based distinction between difficulties within categories
\item
Efficacy of certain distractor methods for a question
\end{enumerate}
With these results, this system (and other systems) would be better able to produce and classify the questions within them, as well as produce more effective distractor methods. However, there are some ethical problems that will need to be addressed in some of this work. Namely, any test for difficulty between students may cause lower test scores than usual or what is considered ``fair", which adversely and unintentionally affects students.
